---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "readme-fig/README-"
)
```


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


[![Build Status](https://travis-ci.org/kota7/gogamer.svg?branch=master)](https://travis-ci.org/kota7/gogamer)

# gogamer: R package for go game data

```{r, fig.height=5, fig.width=5, echo = FALSE}
library(gogamer)
library(magrittr)
stateat(mimiaka, 127) %>% plot()
```


## How to use

Install by

```{r, eval=FALSE}
devtools::install_github("kota7/gogamer")
```

Use by
```{r}
library(gogamer)
```


## What you can do

You can read go game record file in SGF.

```{r}
x <- read_sgf(system.file("extdata/mimiaka.sgf", package = "gogamer"))
class(x)
print(x)
```

You can print the board configuration on console,
```{r}
# argument 'at' specifies the move number
stateat(x, at = 127)
```

or draw as an image.

```{r, fig.height=5, fig.width=5}
plotat(x, at = 127)
```

The image object inherits `ggplot`, 
hence you can save it with `ggsave` function.
```{r, eval=FALSE}
library(ggplot2)
ggsave("goimage.pdf", width = 5, height = 5)
```


You can also draw kifu (game record) image as below.
Again, the object supports `ggsave` function.
```{r, fig.height=5.6, fig.width=5}
plot(kifu(x, from = 1, to = 127))
```


Or you may also print kifu on console.
```{r}
kifu(x, from = 1, to = 127)
```


