---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "readme-fig/README-"
)
```


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


[![Build Status](https://travis-ci.org/kota7/gogamer.svg?branch=master)](https://travis-ci.org/kota7/gogamer)

# gogamer: R package for go game data

```{r, echo=FALSE, fig.height=5, fig.width=5, echo=FALSE, results='hide', message=FALSE}
library(gogamer)
library(magrittr)
stateat(mimiaka, 127) %>% plot() 
```


## Installation and import

Install by

```{r, eval=FALSE}
devtools::install_github("kota7/gogamer")
```

Use by
```{r}
library(gogamer)
```


## Functionalities

### Read sgf files

`read_sgf` reads text files written in sgf format, and compiles as a `gogame` class object.
```{r}
x <- read_sgf(system.file("extdata/mimiaka.sgf", package = "gogamer"))
class(x)
print(x)
```

### Game snapshot

`stateat` function shows the board configuration at an arbitrary move number,
```{r}
# argument 'at' specifies the move number
stateat(x, at = 127)
```

or `plotat` function draws the image.
```{r, fig.height=5, fig.width=5, results='hide', message=FALSE}
plotat(x, at = 127)
```

The image object inherits `ggplot`, 
hence you can save it with `ggsave` function.
```{r, eval=FALSE}
library(ggplot2)
ggsave("goimage.pdf", width = 5, height = 5)
```

Images are fully customizable.
```{r, fig.height=5, fig.width=5, results='hide', message=FALSE}
plotat(x, at = 127, 
       boardcolor = "gray15", gridcolor = "gray85", starcolor = "gray85",
       blackcolor = "black", whitecolor = "white", stonelinecolor = "gray50",
       axislabels = FALSE, lastmovemarker = 2)
```


### Kifu document

`kifu` function creates an one-page kifu object, which prints on the console as below.
```{r}
kifu(x, from = 1, to = 50)
```

`kifuplot` function draws the image.
Again, the object supports `ggsave` function.
```{r, fig.height=5.6, fig.width=5, results='hide', message=FALSE}
kifuplot(x, from = 1, to = 50)
```


