---
title: "graphic test"
author: "Kota Mori"
date: "July 17, 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(gogamer)
library(magrittr)
```


## Changing target width
```{r, fig.width=5, fig.height=5}
plotat(saikoyo, 116, targetwidth = 5)
```

```{r, fig.width=10, fig.height=10}
plotat(saikoyo, 116, targetwidth = 10)
```

```{r, fig.width=3, fig.height=3}
plotat(saikoyo, 116, targetwidth = 3)
```


## Changing colors
```{r, fig.width=5, fig.height=5}
plotat(saikoyo, 116, boardcolor = "pink",
       blackcolor = "green", whitecolor = "orange")
```


## Remove axis label
```{r, fig.width=5, fig.height=5}
plotat(saikoyo, 116, axislabels = FALSE)
```


## Various board size
```{r, fig.width=5, fig.height=5}
ggoban(13) %>% addstones(c(7, 8, 1), c(7, 7, 1), c(1, 2, 1))
ggoban(9) %>% addstones(c(5, 6, 1), c(5, 5, 1), c(1, 2, 1))
ggoban(13, axislabels = FALSE) %>% addstones(c(7, 8, 1), c(7, 7, 1), c(1, 2, 1))
ggoban(9, axislabels = FALSE) %>% addstones(c(5, 6, 1), c(5, 5, 1), c(1, 2, 1))
```


## Territory plot
```{r, fig.width=5, fig.height=5}
x <- read_sgf("../tests/sample/points.sgf")
plotat(x, 100, markpoints = TRUE)
plotat(x, 100, markpoints = TRUE, marklast = FALSE, territoryshape = 22)
plotat(x, 100, markpoints = TRUE, blackcolor = "blue", whitecolor = "red")
plotat(x, 100, markpoints = TRUE, marklast = FALSE, axislabels = FALSE,
       boardcolor = "grey95", whitecolor = "white", blackcolor = "black")
```

## Test for color themes
```{r, fig.width=5, fig.height=5}
plotat(saikoyo, 116, colortheme = "standard")
plotat(saikoyo, 116, colortheme = "dark")
plotat(saikoyo, 116, colortheme = "bw")
plotat(saikoyo, 116, colortheme = "pastel")
plotat(saikoyo, 116, colortheme = "crystal")
```


## Kifu image

### Setting arbitrary start number
```{r, fig.width=5, fig.height=5}
kifu(saikoyo, 11, 20, restart = 1) %>% plot()
```

### Deduct multiple of hundred if appropriate, or disable it
```{r, fig.width=5, fig.height=5}
kifu(saikoyo, 99, 120) %>% plot()
kifu(saikoyo, 100, 120) %>% plot()
kifu(saikoyo, 101, 120) %>% plot()
kifu(saikoyo, 199, 220) %>% plot()
kifu(saikoyo, 200, 220) %>% plot()
kifu(saikoyo, 201, 220) %>% plot()
kifu(saikoyo, 201, 220) %>% plot(adjustorigin = FALSE)
```



### without footnote
```{r, fig.width=5, fig.height=5}
kifu(saikoyo) %>% plot()
kifu(saikoyo) %>% plot(axislabels = FALSE)
```


### with footnote
```{r, fig.width=5, fig.height=5.6}
# fig.width=5, fig.height=5.6
kifu(mimiaka) %>% plot()
kifu(mimiaka) %>% plot(axislabels = FALSE)
```

```{r, fig.width=5, fig.height=6.32}
y <- read_sgf("../tests/sample/ko.sgf")
kifu(y, 1, 108) %>% plot()
```

```{r, fig.width=5, fig.height=5.6}
# check for numbers in the note
kifu(y, 101, 108) %>% plot()
kifu(y, 101, 108) %>% plot(axislabels = FALSE)
```


### For smaller board
```{r, fig.width=5, fig.height=5.96}
# fig.width=5, fig.height=5.96
z <- read_sgf("../tests/sample/ko9.sgf")
kifu(z) %>% plot()
```


### For smaller board with size in the footnote adjusted
```{r, fig.width=5, fig.height=7.58}
# fig.width=5, fig.height=7.58
kifu(z) %>% plot(adjustsizeonnote = TRUE, moveperrow = 4)
```


#### With various number of lines
```{r, fig.width=5, fig.height=5.6}
kifu(z, 1, 15) %>% plot()
# fig.width=5, fig.height=5.6
```

```{r, fig.width=5, fig.height=5.78}
# fig.width=5, fig.height=5.78
kifu(z, 5, 40) %>% plot()
```

```{r, fig.width=5, fig.height=5.78}
# fig.width=5, fig.height=5.78
kifu(z, 3, 12) %>% plot(adjustsizeonnote = TRUE, moveperrow = 4)
```

```{r, fig.width=5, fig.height=6.5}
# fig.width=5, fig.height=6.5
kifu(z, 3, 40) %>% plot(adjustsizeonnote = TRUE, moveperrow = 4)
```


### with color themes
```{r, fig.width=5, fig.height=5.6}
kifu(mimiaka) %>% plot(colortheme = "dark")
kifu(mimiaka) %>% plot(colortheme = "bw")
kifu(mimiaka) %>% plot(colortheme = "pastel")
kifu(mimiaka) %>% plot(colortheme = "crystal")
```


## Partial board
```{r, fig.width=5, fig.height=5}
a <- read_sgf("../tests/sample/tsumego1.sgf")
b <- read_sgf("../tests/sample/tsumego2.sgf")
d <- read_sgf("../tests/sample/joseki.sgf")
```
```{r, fig.width=3, fig.height=4.15}
plotat(a, 0, xlim = c(1, 7), ylim = c(1, 10), targetwidth = 3, quiet = FALSE) 
```
```{r, fig.width=5, fig.height=4.54}
kifu(a, 1, 5) %>% plot(xlim = c(1, 10), ylim = c(1, 9))
```
```{r, fig.width=5, fig.height=6.11}
plotat(b, 0, xlim = c(1, 9), ylim = c(1, 10), quiet = FALSE)
```
```{r, fig.width=5, fig.height=6.11}
kifu(b, 1, 9) %>% plot(xlim = c(1, 9), ylim = c(1, 10))
kifu(b, 1, 9) %>% plot(xlim = c(1, 9), ylim = c(1, 10), axislabels = FALSE)
```
```{r, fig.width=3, fig.height=3}
plotat(d, 10, xlim = c(9, 19), ylim = c(9, 19), targetwidth = 3, quiet = FALSE) 
```

